This recipe can be used without much modification for other vegetables as well. You can replace radish with pumpkin, zucchini and eggplant.

\large{\textbf{Ingredients}}
% \begin{multicols}{2}
  \large{\textbf{Common}}
  \begin{itemize}
    \item White radish \quad\quad\quad\quad \textit{X (Chopped)}
    \item Onion \quad\quad\quad\quad \textit{X (Chopped)}
    \item Tomato (optional) \quad\quad\quad\quad \textit{X (Chopped)}
    \item Oil \quad\quad\quad\quad \textit{X teaspoon}
  \end{itemize}
  % \columnbreak
  \large{\textbf{Indian/special}}
  \begin{itemize}
    \item Ghee (optional) \quad\quad\quad\quad \textit{X teaspoon}
    \item Toor dal \quad\quad\quad\quad \textit{X gram}
    \item Tamarind pulp \quad\quad\quad\quad \textit{$1\frac{3}{4}$ tablespoon}
    \item Asfoetida \quad\quad\quad\quad \textit{1 pinch}
    \item Sambar powder \quad\quad\quad\quad \textit{1 pinch}
  \end{itemize}
% \end{multicols}

\large{\textbf{Recipe}}

\begin{enumerate}
  \item Cook the toor dal (pressure cook in double boiler set up or cook on an open pot for longer while taking care not to let lentils burn at the bottom of the pot) until they are soft and creamy.
  \item Meanwhile, soak the tamarind in warm water. Once it softens, make sure to mash it up so the pulp releases acidity well.
  \item Chop radish (into circular pieces) and some onions (half then quaters or for larger ones, half and then half and one thirds). Its nice to have larger pieces for the taste. Optionally, add a tomato but make sure to adjust the amount of tamarind if the tomatoes are more acidic than sweet.
  \item Add the vegetables into a pot with the tamarind extract (strained roughly to remove large chunks and seeds) and top up with enough water to barely cover the vegetables.
  \item To the pot, add a pinch of asfoetida, salt and 1 teaspoon of sambar powder and let it boil until the vegetables are soft and the raw flavour of the sambar powder is gone.
  \item If the toor dal has been cooked, transfer it to a bowl and mash with a fork or whisk until it is creamy and add it to the pot.
  \item Let the toor dal thicken up the sambar as it boils. Stir occasionally.
  \item When the sambar is nearly done, prepare to temper.
  \item In a small pan heat up some oil (or ghee) and add a teaspoon of mustard seeds and wait till they begin to splutter.
  \item Then, add less than half a teaspoon of funugreek seeds (optional) and a pinch of asfoetida.
  \item If the sambar was not spicy enough, you could also add a dried red chilli or some red chilli powder to the tempering.
  \item Finally add some curry leaves and empty the mixture onto the sambar and turn off the heat.
  \item (NOTE: You could also reverse part of the steps and first start with the steps used for tempering and saute the vegetables in this mixture before adding tamarind extract and water and finally finish with toor dal. This makes for a slightly different flavour overall.)
\end{enumerate}

\large{\textbf{Suggested pairing}}

Serve mixed in rice and with Potato/Colacasia/Brinjal/Raw banana/Yam fry on the side.
